Pre-Analysis Plan: Who Bends and Who Breaks? Experimental Evidence for Conditions Affecting Voters' Evaluations of Politicians Striking Compromises

### 2021-04-21 docs/pap/compromise-punishment-pap.Rmd
update pap

\newpage
# Theoretical Background

@@

## Hypothesis 1

>>>>

\newpage

@@

## Balance Checks
I will conduct a balance test based on demographics (age, gender, education, geographical region, level of urbanness, migration background,  employment, and income), vote choice in the 2021 parliamentary elections, ideological self-placement, political efficacy, attitudes towards women in politics, and positions on the four issues, using the `cobalt` R package [@greifer2021]. 
If the groups are unbalanced on one of these variables -- i.e. standardized mean differences `<0.05` -- I will add the covariates to the analyses.

```{r balance, eval=FALSE, echo = TRUE}
covs <- d %>%
  mutate(treatment = paste(name, compromis, sep = "-")) %>%
  select(treatment, PreT1:PreT8, F1:F9)

balanced <-bal.tab(Treatment ~ PreT1 + PreT2 + PreT3 + PreT4 +
                     PreT5 + PreT6 + PreT7 + PreT8 +
                     factor(F1) + F2 + factor(F9) + factor(F3) +
                     factor(F4) + factor(F5) + factor(F6) + F7 + F8,
                     Age + Education + factor(Sex_str), data = covs,
          thresholds = c(m = 0.05))[[1]]

balanced <- balanced %>%
  mutate(variable = c("Immigration (%)", "Immigration", "Defense", "Education", "Sexism",
                      "Ideology", "Poltical Efficacy", "COVID-19",
                      "Gender: Male", "Age", "Education: Middle", "Education: High",
                      "Region: West", "Region: North", "Region: East", "Region: South",
                      "Little Urban", "Moderatly Urban", "Highly Urban", 
                      "Very Highly Urban", "Migration Background", "Bij1","CDA",
                      "ChristenUnie", "D66", "Denk", "Forum for Democracy",
                      "GroenLinks", "JA21", "PvdA", "Animal Rights Party", "PVV", 
                      "SGP", "SP", "VOLT","VVD", "50Plus Party", "Employment",
                      "Income"),
         variable = factor(variable,
                           levels = c("Immigration (%)", "Immigration", "Defense",
                                      "Education", "Sexism", "Ideology", 
                                      "Poltical Efficacy","COVID-19", 
                                      "Gender: Male", "Age", "Education: Middle",
                                      "Education: High", "Region: West", "Region: North",
                                      "Region: East", "Region: South",
                                      "Little Urban", "Moderatly Urban", "Highly Urban",
                                      "Very Highly Urban", "Migration Background",
                                      "Bij1","CDA", "ChristenUnie", "D66", "Denk", 
                                      "Forum for Democracy", "GroenLinks", "JA21", 
                                      "PvdA", "Animal Rights Party", "PVV", 
                                      "SGP", "SP", "VOLT","VVD", "50Plus Party",
                                      "Employment", "Income")),
         difference = Diff.Un,2) %>%
  select(variable, difference) %>%
  ggplot(aes(x = variable, y = difference)) +
  geom_point(size = 3, colour = "gray55") +
  theme_bw() +
  labs(x="", y= "Standardized Mean Differences") +
  ggtitle("Covariate Balance") +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = 0.05, linetype = "dashed") +
  geom_hline(yintercept = -0.05, linetype = "dashed") +
  coord_flip()
```

## Hypothesis 1
I test the hypotheses formulated in [Section 1](#expectations) applying a multiverse approach [@steegen2016increasing;@simonsohn2019specification] using the `specr` R package [@masur2020specr].
Instead of running various models using the different dependent variables
